\huge A Usability Evaluation of Tor Launcher

### 2016-11-18 pets2017-paper/pets2017-paper.tex
pass through paper. definitely procrastinating on related work.

We hope that our work contributes to Tor Browser and provides an interesting case study. We also encourage the use our evaluation pipeline and methods for evaluating other user-facing interfaces and features.

@@

\section{Background}
\label{sec:background}
This section covers technical background necessary to understand the study.

\subsection{Relays, Bridges, Pluggable Transports, and Proxies}

 A user uses the Tor network to indirectly connect to websites using Tor Browser. The Tor network is a group of routers that peform onion routing, a technique for anonymous communication over a computer network.  Tor relays are the routers in the Tor Network. 
Guard relays that serve as an entry node into the Tor network and receive packets from the user. Middle relays forward traffic from an entry relay to an exit relay, and provide an extra layer of encryption in the Tor network. Exit relays receive traffic from a middle relay, and direct the traffic to its intended destination.

Bridges are unlisted Tor relays that serve as an alternative entry node.
Bridges can be unlisted relays that behave similarly to a regular Tor relay,  
but most run a pluggable transport (referred to as ``transport'' for shorthand) that obfuscates traffic. 
Pre-configured bridges can be selected by ``Transport type,'' which refer to various
censorship circumvention technologies (``pluggable transports'').
Most transports rely on the secrecy of their static IP addresses for their effectiveness.
These include ``fte'' and ``fte-ipv6''~\cite{fte},
which disguise the Tor protocol as another protocol (such as HTTP), and
``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
which encrypt or alter the Tor protocol to appear as random noise.
Other transports route traffic through other services and do not need secret IP address. 
``flashproxy''~\cite{flashproxy} connects through third party web browsers,
and the ``meek''~\cite{fifield2015blocking} options route traffic
through content delivery networks. Fig.~\ref{fig:old-bridge-combobox} shows the bridge and transport options at the time of the study.

In this paper, the word``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy. This is to maintain consistency with the wording in the configuration interface. Fig.~\ref{fig:topology} illustrates the interacting components. We recognize that, a proxy is technically anything that acts as an intermediary between clients and servers. By this definition, a single Tor relay, a bridge, the circuit of entry, middle, and guard relays, and local proxies can all can be considered a proxy.

\subsection{State and Corporate Censorship}
State level censors block access to the Tor network by blocking Tor relays, which are publicly listed. Some also employ more sophisticated techniques such as deep packet inspection and protocol detection. This means that users can connect directly to websites, but some may be blocked as is Tor. The thoroughness of censorship is what requires different bridges and transports.

A local proxy is required to connect in certain managed networks (i.e. company and university firewalls). This usually means that users cannot connect to the Internet at all without a proxy, including connecting to the Internet through Tor. The user must be able to connect to the Internet through their proxy before trying to connect to the Internet with Tor.

\subsection{Connecting to Tor} 
Configuring a bridge requires providing a
``bridge line,'' a specifically formatted bridge specification that
includes its IP address, transport type, and other metadata.
The interface has hard-coded options (see Figure~\ref{fig:old-bridge-combobox}) 
that select a group of bridges that use a particular transport.
For instance, choosing the hard-coded obfs3 option
configures a handful of bridges that use the obfs3 transport.
If the built-in bridges do not work, a user can obtain bridge lines
through out-of-band channels, for instance by email~\cite{bridgedb}.

There are many valid configuration settings to connect to the Tor network.
A user who needs a bridge can connect to Tor with a bridge and proxy, provided that both were configured correctly.

@@

\subsection{Testing Pipeline} 
Two researchers first performed a cognitive walkthrough~\cite{cognitive-walkthrough} to prepare for user testing. A cognitive walkthrough is evaluation method that requires usability evaluators to work through a series of tasks from the perspective of the user, usually to understand a system's learnability for new or infrequent users.

@@

We opportunistically used our observations to make changes to the interface. We believed that the process of identifying design principles, drafting design changes, and testing an alternative interface would be insightful and have the potential to discover impactful changes.

@@

Task time is a supplemental usability metric that measures user productivity during the task. We measured task time two different ways. Connection time measures how long users use the configuration interface, which includes time  spent waiting while a Tor Browser establishes a connection to Tor, which can dominate the measurement. Configuration time measures the time users spent actively configuring bridges and proxies.

@@

We used Windows Firewall rules to block IP addresses of public Tor relays (E2, E3) and default bridges (E3). 
We used the Windows operating system hosts file to to block websites by
mapping domain names to localhost (127.0.0.1) (E1, E2, E3). We blocked torproject.org and its subdomains to discourage downloading Tor Browser, as we had installed a specific version on the test computers.  We blocked wikipedia.org, cnn.com, and their subdomains to create ``censored'' sites for the experiment.

@@

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% identified as male and 50\% identified as female. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). One participant declined to report their age, so age calculations omit one participant's information. 100\% had at least some college education. We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}). We verified their self-reported familiarity with Tor Browser in-person to identify new users, and found that 12 were new users and 4 had previously used Tor Browser in some capacity.

@@

We distributed participants evenly across experimental conditions:  5~in E1, 5~in E2, and 6~in E3. Although there is variation in gender, age, ``technical expertise,'' and ``use of security tools'' in each experimental condition, we ensured each condition had a participant who used Tor Browser before.

\subsection{Setup} 
We ran the experiment in a meeting room in <redacted building> at <redacted university>. The room had a desk and chair, where a monitor, keyboard, and a Windows 8 computer were set up. On a clean computer, we manually downloaded and installed the necessary software for the experiment: Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer to allow users to browse the Internet on a another browser of their choice, and VLC to record the screen during the experiment. Before each participant entered the room, we ran a script on the computer that
set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.

\subsection{Procedure}
Three researchers ran the formative usability testing, with each session having at least two researchers.  
Before the experiment began, each participant was verbally informed of the purpose of the 
study, what data was collected, and any associated risks. If they wished to participate,
they were informed again in writing and consented by signing the document. To be thorough, 
we clarified verbally that they could stop at any time during the experiment with no negative consequences.

The experiment formally began by informing the participant of the simulated censorship environment (Appendix~\ref{qualitative-script}). This purpose of this introduction was to clarify that the main task
was to connect to Tor, rather than figuring out if they needed to connect to Tor. 
We instructed them to visit a blocked and unblocked website
in a non-Tor browser to clarify that the Internet was functioning as expected. 
We then told them to use Tor Browser to visit a censored site and pointed out 
the respective shortcut on their desktop.

We then asked them to complete a worksheet (Appendix~\ref{participant-worksheet}) that 
required answers from one blocked website (Wikipedia) and one non-blocked website (CNN).
The worksheet did not specify which website was censored. 
We chose these websites because they are popular websites and that their likely familiarity 
would make the task seem less intimidating.

Participants were given 45 minutes to complete their worksheet. 
After instructions, the researchers left and watched a live feed of the participants' screen in another room to minimize interactions.

After participants completed the browsing tasks (or ran out of time),
we asked them standard interview questions about their experience (Appendix~\ref{interview-questions}) and took notes of their responses. We then followed up with participant-specific questions to verify any hypotheses   we had from observation (e.g. ``the participant was selecting bridges at random''). We paid each participant~\$30 for their time.

\subsection{Results} 
We give a summary of what our participants did below. We watched the screen recording to summarize their actions and referred to their interviews for insight into why they took specific actions. We hope that these participant summaries give some insight into how users may currently struggle with the Tor Launcher interface.

@@

%P4(regular): E1 (8:56, 7:22 to 16:18)
\pquote{P4 (new user, obfs4, 8:56)}{They chose the recommended bridge and then tried to configure a proxy. After not being able to fill out the proxy input fields, they start over and connected using an obfs4 bridge. Note that they didn't try connecting with the obfs3 bridge, which would have worked.}

%P10 (has used Tor before): E1 (1:02; 0:13 to 1:15)
\pquote{P5 (previous Tor user, obfs3, 1:02)}{They connected using the recommended bridge.}

Participants in E1 were able to connect to Tor, but most were unsure if their actions were correct. Three of the five participants unnecessarily used bridges.

\subsubsection{E2} 
In E2, a bridge was required to connect, but any bridge worked. Configuring a proxy was optional.
Observations in E2:

%P7 (heard of Tor): E2 (4:04; 0:29 to 4:33) 
\pquote{P6 (new user, obfs3, 4:04)}{They tried connecting directly and gave up after minutes of waiting. Then, they connected using the recommended bridge.}

%P13 (regular): E2 (7:48; 0:34 to 9:22) 
\pquote{P7 (new user, obfs3, 9:22)}{They tried connecting directly. They restarted Tor Launcher and tried another direct connection---and repeated this two more times. On the fourth restart, they tried to configure a proxy, but gave up. On the fifth restart, they connected using the recommended bridge.}

%P12 (regular): E2 (10:40; 0:46 to 11:26)
\pquote{P8 (new user, direct, 10:40)}{They tried connecting directly. They then looked at proxy settings, gave up, and tried connecting directly again. Then, they tried to configure a proxy, and gave up. They tried a direct connection again, which worked unexpectedly. They found a bug in our setup that we fixed for the later experiment. E2 required a bridge to connect, but new public relays came online after we ran our firewall rules and they were able to connect using those new relays. }

%P11 (used Tor before): E2 (~3:00; 1:05 to 5:13)
\pquote{P9 (previous Tor user, obfs3, 4:08)}{They tried connecting directly. Then, they answered no to both bridge and proxy questions, and effectively tried another direct connection. After that, they connect using the recommended bridge.}

%P8 (used Tor): E2 (clock drift mission impossible, 1:38 to 7:20) 
\pquote{P10 (previous Tor user, failed to connect)}{They tried a direct connection. Then, they tried a connection with the recommended bridge, which should have worked. However, our setup experienced a clock drift. Tor does not allow connections with bad clocks. They spent the rest of their time trying different bridges and proxies in vain (Figure~\ref{fig:proxy-attempt}).}

Participants in E2 {\it eventually} connected using the recommended bridge, but spent a fair bit of time waiting for direct connections to fail and unsuccessfully configuring proxies.

\subsubsection{E3}
In E3, a bridge was required to connect, but only meek and custom bridges worked. Configuring a proxy was optional.
Observations in E3:

@@

%P16: E3 (regular) FAIL (why did obfs3 work the first time? It shouldn't have!) 
\pquote{P13 (new user, failed to connect)}{They tried connecting directly, and then with the recommended bridge. They retried connecting with the recommended bridge. When that didn't work, they tried to configure a proxy. Then, they gave up and tried using other browsers to complete the task.}

@@

%P1 (heard of tor before): E3 (~7:31, 0:51 to 8:22) 
\pquote{P15 (new user, meek-azure, 7:31)}{They tried connecting directly, and then with the recommended bridge. After that, they tried a connection using a meek-azure bridge, but gave up after before it could connect. They went back to the start screen and clicked connect, which made a connection using meek-azure bridge. The participant thought they made a direct connection, but the connect button used settings toggled in the bridge and proxy screens in the interface.}

%P5 (has used tor before): E3 (22:06; 0:00 to 22:06)
\pquote{P16 (previous Tor user, custom bridge, 22:06)}{They tried and retried connecting directly, then they tried connecting with the recommended bridge. After briefly looking at error messages the system log, they retried connecting directly two more times. After looking up proxy settings, they tried connecting with a meek-google bridge, but gave up before it could connect. They made a connection with the custom bridge by following the instructions from the bridge help button (they created a throwaway email account, emailed the bridge responder with poor syntax and did not get a response, emailed the bridge responder again with correct syntax and got a response, and then typed in the bridge information into the custom bridge field).}

Participants in E3 struggled. Three failed to connect. Of the three that connected, one brute forced options until something worked (P14), another did not understand what they did (P15), and the third used a custom bridge after being convinced meek bridges were not working (P16).

@@

Participants found the interface confusing, and were often intimidated by the tasks they were asked to do.

@@

Participants were unsure of what to do, and often configured bridges and proxies when they did not need to.

%P15 in the repo, but P12 in the paper
\pquote{P15}{``I didn't know if this computer had any proxy information. I wasn't able to find it if it did.''}

The progress bar had system dependencies that made it update oddly. If progress bar reached a 90\% and failed, the progress bar will remain at 0\% on the next attempt until the progress surpassed 90\%. Many assumed that their subsequent attempts were wrong because of this.

%P1 in the repo, P15 in the paper
\pquote{P15}{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.''}

We think users in the wild may also face these challenges, and that changes should be made to mitigate them. We show our attempt in the next section.

@@

\subsection{Procedure} 
Three researchers agreed on security and usability design principles. 
We then rewatched screen capture videos and read interview transcriptions to brainstorm design changes. We provided the security and usability design principles, screen capture videos, interview transcriptions, and our suggested changes to a user interface designer, who iteratively redesigned the interface with our feedback and user interface best practices in mind. Figure~\ref{fig:new-interface} shows our redesign of the interface.

@@

In addition to addressing the pain points we discovered through our formative usability testing (Section~\ref{sec:pain-points}), we aimed to follow usability best practices by minimizing work, giving targeted feedback, and helping users build an understanding of the system.

\subsection{Changes Made} 
We made these changes for a more usable interface. \\

\noindent To minimize work: 
\begin{itemize}
\item We eliminated technical questions, resulting in fewer tasks and interface screens. 
\item We simulated auto-detection for proxies, telling users that they did not need a proxy. This is feasible to do with a local scan (no information leaked). 
\item We labeled the configure button as an option for users in heavily censored environments.
\item We gave advice on choosing transports, telling users to try a meek bridge if obfs3 does not work.
\end{itemize}

To give targeted feedback: 
\begin{itemize}
\item We fixed the progress bar so that it reflects the current progress on subsequent attempts. 
\item We switched added indicators to the progress bar to show the progress of bridges and proxies. 
\item We told users what to try next on errors (i.e. choose a different bridge, try a without a proxy). 
\end{itemize}

To build an understanding of the system:
\begin{itemize}
\item We added a summary screen displays the current bridge and proxy settings for system visibility. 
\item We switched proxy and bridge screens to put them in a topologically sequential order (Figure~\ref{fig:topology}).
\end{itemize}

Figure~\ref{fig:new-interface} shows the resulting interface.  Figure~\ref{fig:old-interface} shows the unchanged version.

@@

\subsection{Recruitment}
We recruited  people using the recruitment text in Appendix~\ref{quantitative-recruitment}. We recruited 65 participants from Craigslist and 59 participants from the <redacted lab> participant pool. <Redacted lab> encouraged the use of their participant pool, but we bargained to recruit participants from Craigslist to ensure a diverse set of participants. Although the <redacted lab>'s participant pool is not limited to students and staff from <redacted institution>, it was estimated that a large majority were.

124 people participated in our experiment, but we used data from 114. We filtered participants who made errors in completing the consent form or did not interact with the instrumented interface. Of the 114, one participant did not report their demographics. We still use their experiment data. Of the 113, 44.2\% identified as male, 54.0\% identified as female, and 1.8\% identified as neither. Ages ranged from 18 to~68 years ($\mu = 28.2$, $\sigma = 12.3$). 84.1\% of our participants had at least a college education. We distributed participants evenly across experimental condition, about 20 in each interface and environment combination. Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craigslist recruited participants and half <redacted lab>  pool participants.

\subsection{Setup}
We ran our experiment at <redacted lab>, an experimental social science laboratory for behavioral experiments. The testing room had 36 workstations with identical Windows~7 laptops. Side panels at each workstation to discouraged participants from looking at other participants' screens. 
%Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
The computers at <Redacted lab> use a system restore software to revert computers to a clean version at the beginning of each session.

>>>>

We hope that our work contributes to Tor Browser and is an informative case study of users interacting with anonymity and censorship circumvention tools.

\section{Background}
\label{sec:background}
This section discusses network components, when to configure them, and how they connect to Tor.

\subsection{Proxies, Relays, Bridges, and Pluggable Transports}

In this paper, the word``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy. This is to maintain consistency with the wording in the configuration interface. Fig.~\ref{fig:topology} illustrates the interacting components. A proxy is technically an intermediary between clients and servers, so a single Tor relay, a bridge, the circuit of entry, middle, and guard relays, and local proxies can all can be considered a proxy. A user uses a proxy to bypass local firewalls.

Tor relays are the routers in the Tor network. The Tor network is a group of routers that peform onion routing, a technique for anonymous communication over a computer network.  
Guard relays that serve as an entry node into the Tor network and receive packets from the user. Middle relays forward traffic from an entry relay to an exit relay, and provide an extra layer of encryption in the Tor network. Exit relays receive traffic from a middle relay, and direct the traffic to its intended destination. 
A user uses Tor Browser to connect to the Tor network, which indirectly connects to websites.

Bridges are unlisted Tor relays that serve as an alternative entry node.
Bridges can be unlisted relays that behave similarly to a regular Tor relay,  
but most run a pluggable transport (referred to as ``transport'' for shorthand) that obfuscates traffic. 
Pre-configured bridges can be selected by ``Transport type,'' which refer to various
censorship circumvention technologies (``pluggable transports'').
Most transports rely on the secrecy of their static IP addresses for their effectiveness.
These include ``fte'' and ``fte-ipv6''~\cite{fte},
which disguise the Tor protocol as another protocol (such as HTTP), and
``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
which encrypt or alter the Tor protocol to appear as random noise.
Other transports route traffic through other services and do not need secret IP address. 
``flashproxy''~\cite{flashproxy} connects through third party web browsers,
and the ``meek''~\cite{fifield2015blocking} options route traffic
through content delivery networks. Fig.~\ref{fig:old-bridge-combobox} shows the bridge and transport options at the time of the study. A user uses a bridge to connect to the Tor network while Tor relays or the Tor network protocol is is being censored.

\subsection{State and Corporate Censorship}
A local proxy is required to connect in certain managed networks (i.e. universities and corporations). This usually means that users cannot connect to the Internet at all without a proxy, including connecting to the Internet through Tor. The user must first successfully connect to the Internet through their proxy before trying to connect to a Tor relay or bridge.

State level censors block access to the Tor network by blocking pubicly listed Tor relays. Some also employ more sophisticated techniques such as deep packet inspection and protocol detection. This means that users can connect directly to websites, but some may be blocked as is Tor. The thoroughness of censorship is what requires different bridges and transports.

\subsection{Connecting to Tor} 
A ``bridge line,'' a specifically formatted bridge specification that
includes its IP address, transport type, and other metadata 
officially configures Tor Browser to use bridges.
Users can do this more easily by choosing a 
a hard-coded option in the interface (see Figure~\ref{fig:old-bridge-combobox}) 
that select a group of bridges that use a particular transport.
For instance, choosing the hard-coded obfs3 option
configures a handful of bridges that use the obfs3 transport.
If the built-in bridges do not work, users can obtain bridge lines
through out-of-band channels~\cite{bridgedb}.

There are many valid configuration settings to connect to the Tor network.
A user who does not need a bridge or proxy can connect with a bridge, proxy, or both, provided that they are configured correctly.

@@

@@

\subsection{Testing Pipeline} 
We performed a cognitive walkthrough~\cite{cognitive-walkthrough} to prepare for user testing. This evaluation method involved usability evaluators to working through a series of tasks from the perspective of the user, trying to understand a system's learnability for new or infrequent users.

@@

We opportunistically used our observations to make changes to the interface. We believed that the process of identifying design principles, drafting design changes, and testing an alternative interface would be insightful.

@@

Task time is a supplemental usability metric that measures user productivity during the task. We measured this in two ways. Connection time measures how long users took to connect to Tor, which includes time spent waiting for Tor to configure relays for the user. This can take up to a couple minutes and dominate the measurement. Configuration time measures the time users spent configuring bridges and proxies.

@@

We conducted our studies at <redacted>, which only had Windows machines. 
So we used Windows Firewall rules to block IP addresses of public Tor relays (E2, E3) and default bridges (E3). 
and the Windows operating system hosts file to to block websites by
mapping domain names to localhost (127.0.0.1) (E1, E2, E3). For all experiments, we blocked torproject.org and its subdomains to discourage downloading Tor Browser (as we had installed a specific version on the test computers) and wikipedia.org, cnn.com, and their subdomains (these were our simulated ``censored'' websites).

@@

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked a prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} so that we could have a diversity of gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% identified as male and 50\% identified as female. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). One participant declined to report their age, so age calculations omit this participant's information. All of our users were highly educated, having at least some college education. We show their self-reported familiarity with technical terms use of security tools in  Appendix~\ref{prescreening-responses}. We verified their self-reported familiarity with Tor Browser in-person to identify new users, and found that 12 were new users and 4 had previously used Tor Browser in some capacity.

@@

We distributed participants evenly in number across experimental conditions:  5~in E1, 5~in E2, and 6~in E3. We ensured that each condition had a participant who had used Tor Browse before, and tried for some variation in gender, age, ``technical expertise,'' and ``use of security tools'' in each experimental condition as well.

\subsection{Setup} 
We ran the experiment in a meeting room in <redacted building> at <redacted university>. The room had a desk and chair, where a monitor, keyboard, and a Windows computer were set up. On a clean computer, we manually downloaded and installed the necessary software for the experiment: Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in a another browser of their choice, and VLC to record the screen during the experiment. Before each participant entered the room, we ran a script on the computer that
set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.

\subsection{Procedure}
Three researchers ran the formative usability tests, with each session having at least two researchers.  
We told the participant the purpose of the 
study, what data was collected, and any associated risks. 
Then they signed a consent form with this information in writing. 
Before the experiment, we clarified that they could stop at any time during the experiment with no negative consequences.

We started by informing the participant of the simulated censorship environment (Appendix~\ref{qualitative-script}) and task. We explicitly stated that the they should use Tor to circumvent censorship. 
We instructed them to visit sample censored and uncensored websites
in a non-Tor browser to clarify that the Internet was functioning and
pointed out the Tor Browser shortcut on their desktop.

They were asked to complete a worksheet (Appendix~\ref{participant-worksheet}) that 
required answers from Wikipedia (censored) and CNN (uncensored).
We chose these websites because their likely familiarity~\ref{alexa}
would make the task seem less intimidating. They were given 45 minutes to complete the task. 
After instructions, researchers left to minimize interactions and watched a live feed of the participants' screen from another room.

After they completed the worksheet (or ran out of time),
we asked them general questions about their experience (Appendix~\ref{interview-questions}) and participant-specific questions to verify any hypotheses we had (e.g. ``the participant was selecting bridges at random''). We paid each participant~\$30 for their time.

\subsection{Results} 
We use out screen recording and interview data to give a summary of each participant.

@@

%P4(regular): E1 (8:56, 7:22 to 16:18)
\pquote{P4 (new user, obfs4, 8:56)}{They chose the recommended bridge and then tried to configure a proxy. After not being able to fill out the proxy input fields, they started over and connected with an obfs4 bridge. Note that they did not try connecting with the obfs3 bridge, which would have worked.}

%P10 (has used Tor before): E1 (1:02; 0:13 to 1:15)
\pquote{P5 (previous Tor user, obfs3, 1:02)}{They connected with the recommended bridge.}

Participants in E1 were able to connect to Tor, but most were unsure if their actions were correct. Three of the five participants unnecessarily configured bridges.

\subsubsection{E2} 
In E2, a bridge was required to connect. Any of the hardcoded bridges from the dropdown menu, as well as any custom bridges aquired out of band would work. Configuring a proxy was optional.
Observations in E2:

%P7 (heard of Tor): E2 (4:04; 0:29 to 4:33) 
\pquote{P6 (new user, obfs3, 4:04)}{They tried connecting directly. After watching the progress bar not make any progress for a couple minutes, and gave up on the direct connection. Then they connected with the recommended bridge.}

%P13 (regular): E2 (7:48; 0:34 to 9:22) 
\pquote{P7 (new user, obfs3, 9:22)}{They tried connecting directly. They restarted Tor Launcher and tried to connect directly again---and repeated this two more times. On the fourth restart, they tried to configure a proxy, but gave up. On the fifth restart, they connected using the recommended bridge.}

%P12 (regular): E2 (10:40; 0:46 to 11:26)
\pquote{P8 (new user, direct, 10:40)}{They tried connecting directly. After waiting a couple minutes, they figured that did not work and looked at proxy settings. But after looking at the settings and being intimidated, they tried connecting directly again. Then, they tried to configure a proxy, and gave up. They tried connecting directly again, which worked unexpectedly. They found a bug in our setup that we fixed for the later experiment. E2 required a bridge to connect, but new public relays came online after we ran our firewall rules and they were able to connect using those new relays. }

%P11 (used Tor before): E2 (~3:00; 1:05 to 5:13)
\pquote{P9 (previous Tor user, obfs3, 4:08)}{They tried connecting directly. And they tried connecting directly through a different user path by answering no to bridge and proxy questions in the interface, connecting from the proxy screen. Then, they connected using the recommended bridge.}

%P8 (used Tor): E2 (clock drift mission impossible, 1:38 to 7:20) 
\pquote{P10 (previous Tor user, failed to connect)}{They tried a direct connection. Then, they tried a connection with the recommended bridge, which should have worked. However, our setup experienced a clock drift. Tor does not allow connections with bad clocks. They spent the rest of their time trying different bridges and proxies in vain (Figure~\ref{fig:proxy-attempt}). This participant tried the most attempts to connect to Tor, using a variety of bridges and proxies.}

Participants in E2 tried a direct connection to Tor before {\it eventually} connecting with the recommended bridge.
They spent a fair amount of time waiting before determining that connections failed. Some stated that they connected directly because the interface says that it would work in ``most situations'' (Figure~\ref{fig:old-first}). Our participants did not know if they needed bridges or proxies, so they only tried to configure one when the direct connection failed. Since they did not know whether they needed a bridge or proxy, they often tried to configure proxies when they did not need one and should have configured bridges instead.

\subsubsection{E3}
In E3, a bridge was required to connect. Most of the hardcoded bridges in the dropdown menu do not work, with the exception of meek-amazon, meek-azure, and meek-google. Custom bridges can also work. Configuring a proxy was optional.
Observations in E3:

@@

%P16: E3 (regular) FAIL
\pquote{P13 (new user, failed to connect)}{They tried connecting directly, and then with the recommended bridge. They retried connecting with the recommended bridge. When that didn't work, they tried to configure a proxy. Then, they gave up on the task entirely.}

@@

%P1 (heard of tor before): E3 (~7:31, 0:51 to 8:22) 
\pquote{P15 (new user, meek-azure, 7:31)}{They tried connecting directly, and then with the recommended bridge. After that, they tried a connection using a meek-azure bridge, but gave up after before it could connect. They went back to the first screen~\ref{fig:old-first} and clicked connect, which made a connection using meek-azure bridge. The connect button makes a connection to Tor with the toggled settings in the interface. When the interface is initialized to not use a bridge or proxy, clicking connect on the first page starts a direct connection. But since the participant had chosen a meek-azure bridge, the connect button made a connection to a meek-azure bridge, even though the text in the first screen says that they will ``connect directly.'' Because of this, the participant thought they made a direct connection. Although they succeeded in connecting to Tor, they did not realize what they had done or why connecting to a meek-azure bridge worked. They chose that bridge at random.}

%P5 (has used tor before): E3 (22:06; 0:00 to 22:06)
\pquote{P16 (previous Tor user, custom bridge, 22:06)}{They tried and retried connecting directly, then they tried connecting with the recommended bridge. After briefly looking at error messages the system log, they retried connecting directly two more times. After trying to configure a proxy for a while, they instead decided not to use one and tried connecting with a meek-google bridge, which would have worked. But  due to a bug in the progress bar that prevents it from updating correctly on subsequent attempts, they gave up before it could connect. They made a connection with the custom bridge by following the instructions from the bridge help button (they created a throwaway email account, emailed the bridge responder with poor syntax and did not get a response, emailed the bridge responder again with correct syntax and got a response, and then typed in the bridge information into the custom bridge field).}

Participants in E3 also generally tried a direct connection to Tor. They did not know if they needed a bridge or proxy, and like the participnts in E2, only configured them when the direct connection failed. But even if the participants were able to figure out that they needed a bridge and not a proxy, the recommended bridge will not work. Of the participants that failed, they all tried the recommended bridge but not any others. The participants that did manage to connect to Tor did not know which bridges worked and which ones did not, or which ones to try next in case the recommended one failed. P14 brute forced options until something worked, P15 did not think that thye used a bridge, and P16 gave up on a hardcoded bridge that would have worked and used a custom bridge instead.

@@

The interface uses a technical and Tor-specific terms that are unfamiliar to an average user, such as the Tor network, internet service provider (ISP), local proxy, bridges, and transports. Participants found the interface confusing, and were often unable to answer the questions that were designed to guide them (Figures~\ref{fig:old-bridge} and~\ref{fig:old-proxy}) and did not know what to do to configure bridges and proxies (Figures~\ref{fig:old-bridge-combobox} and~\ref{fig:old-proxy-yes}).

%P13 in the repo, P7 in the paper 
\pquote{P7}{``I didn't know where to start. I didn't know what to do. [I] was just fiddling, to be honest with you... it was kind of confusing.''}

In addition to not knowing what to do, they did not understand the choices that they had to make.

%P2 in the repo, P2 in the paper 
\pquote{P2}{``I don't know what any of those (points to list of transports) means. I don't know what that (points to proxy settings) means at all."}

@@

%P15 in the repo, but P12 in the paper
\pquote{P15}{``I didn't know if this computer had any proxy information. I wasn't able to find it if it did. I went to every browser and could not find what they were talking about. I googled how I would find that and couldn't seem to get good information. [I] couldn't find anything that said tools.''}

%P11 in the repo, P9 in the paper
\pquote{P9}{``I think you can only answer this question correctly if you know what a local proxy is.
Otherwise you have no chance... because looking at the internet setting in another browser could be anything.''}

The progress bar had dependencies that made it update oddly. If progress bar reached a 90\% and failed, the progress bar will remain at 0\% on the next attempt until the progress surpassed 90\%. This made many assume that their subsequent attempts were wrong.

%P13 in the repo, P7 in the paper 
\pquote{P7}{``I was kind of doubting myself because everything was really slow.''}

%P16 in the repo, P13 in the paper
\pquote{P13}{``Put in a 30 second timeout! I don't know, maybe it takes longer than that...''}

%P1 in the repo, P15 in the paper
\pquote{P15}{``there doesn't seem to be any timeout on any of this stuff. Am I waiting long enough? Should I wait 5 minutes?''}

We have additional concerns on system visibility, error recovery, and user workload. Users cannot see their settings before or while they are connecting. This is only visible on the bridge and proxy screens. Participants did not know what to do after a connection failed. Users should be made aware of what to fix. Users do too much work (reading text, click throughs, choices) in this interface. We show an attempt to fix these issues in Section~\ref{sec:design}.

@@

\subsection{Procedure} 
We agreed on security and usability design principles, before reviewing our formative usability study observations and brainstorming changes to the interface. We worked with a user interface designer to iteratively design the interface. Figure~\ref{fig:new-interface} is the result.

@@

In order of priority, our design objectives were to minimize the user workload, to assist in user decision making, and to help users understand the system. We preferred to eliminate tasks if we could, help users through necessary tasks, and educate them only if this information would be useful for future decisions. These objectives were inspired by our previous usability study.

\subsection{Changes Made} 
To require our users to do less work, we eliminated the bridge and proxy questions from Figure~\ref{fig:old-bridge} and~\ref{fig:old-proxy} and simulated auto-detection for proxies by telling users that they did not need a proxy (this is feasible to implement with a local scan that does not leak information.

To help users decide what to do, we labeled the configure button as an option heavily censored environments, tell users to configure a bridge if Tor is censored, and gave additional advice on choosing transports if the recommended one did not work.

To help users understand what is going on, we added a summary screen displays the current bridge and proxy settings for system visibility, switched proxy and bridge screens to put them in a topologically sequential order (Figure~\ref{fig:topology}), and added checklist indicators of components topological order into the progress bar to that show if various components reached successfully.

@@

\subsection{Recruitment}
We recruited 65 participants from Craigslist and 59 participants from the <redacted lab> participant pool using text in Appendix~\ref{quantitative-recruitment}. <Redacted lab> encouraged the use of their participant pool, but we bargained to recruit participants from Craigslist to ensure a diverse set of participants. <Redacted lab>'s participant pool is mainlystudents and staff from <redacted institution>, even though anyone could join.

We had 124 participants, but we filtered out 10 participants who did not complet the consent form correctly or did not interact with the instrumented interface. Of the 114, one participant did not report their demographics. We still use their experiment data. Of the 113, 44.2\% identified as male, 54.0\% identified as female, and 1.8\% identified as neither. Ages ranged from 18 to~68 years ($\mu = 28.2$, $\sigma = 12.3$). 84.1\% of our participants had at least a college education. We had about 20 in each interface and environment combination and ensured each condition had about half Craigslist recruited participants and half <redacted lab>  pool participants.

\subsection{Setup}
We ran our experiment at <redacted lab>, an experimental social science laboratory for behavioral experiments. The testing room had 36 workstations with identical Windows~7 laptops. Side panels at each workstation to discouraged participants from looking at other screens. 
%Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
The computers at <Redacted lab> use a system restore software to revert computers to a clean version at the beginning of each session.

Before each session, we ran a script that downloaded Firefox, Chrome, IE, and VLC, set up one of the three simulated environments (E1, E2, or E3), and downloaded a version of Tor Browser 5.0.3 (original or our design), and started the computer screen recording. In contrast to the previous test, the Tor Browser 5.0.3 was instrumented to log user interactions with it (clicks, selects, transitions, etc.). Each computer was manually assigned one of the six interface--environment combinations in a way that evenly distributed experimental conditions throughout the room.

\subsection{Procedure}
We assigned participants  to a simulated censorship environment combination at random by being assigning them to a computer at random. We told the participants the purpose of the study, what data was collected, and any associated risks. Then they signed a consent form with this information in writing. Before the experiment, we clarified that they could stop at any time during the experiment with no negative consequences.

We started by informing participants of the simulated censorship environment, giving them their worksheet,  informing them that Tor browser is necessary to circumvent censorship, and pointing out that Tor is installed for them on the computer (Appendix~\ref{quantitative-script}). They were asked to complete a worksheet that requires an answer from a censored site (Wikipedia) and explicitly reminds users to use Tor to do so (Appendix~\ref{summative-worksheet}). We reminded them to not show personal information since we are recording their screens, answered any questions, then gave them 40 minutes to complete the task.

After instructions, researchers maintained minimal interactions with the participants, only answering logistical questions. Afterward, we administered an exit survey to collect demographics (Appendix~\ref{quantitative-exit-survey}). We paid each participant \$30 for their time.
